
%% \skills{Master of Science in Aerospace Engineering}, \textit{Technical University of Delft (TUDelft)}	\hfill 09 2019 


\subsection{{Master of Science in Aerospace Engineering} \hfill 09 2019 --- }
\subtext{Technical University of Delft (TUDelft) \hfill Delft, Zuid Holland, The Netherlands}
\begin{zitemize}
\item Specialization: Space Flight, Space Exploration
\item Key courses: Multi-Disciplinary optimisation; Astrodynamics, optimisation in Astrodynamics, Numerical Astrodynamics, Mission Geometry and Orbit Design, Planetary Sciences, Space Systems Engineering. 
\item Key projects: \begin{zitemize}
\item Preliminary design of a \textit{scientific mission to explore the centaur Chariklo}.
\item Systems requirements analysis of an \textit{asteroid mining mission}: mission and need statement, stakeholders analisys, acceptance criteria, concept design, and risk analysis.
\item Design of an \textit{Earth Observation mission} required to analyse sea-level variance for a span of 10 years. Ground-repeating-tracks were used, as well as a literature research to find similar missions, and design trades.
\item \textit{Shape Design optimisation of an Earth re-entry system}: propagating the equations of motion, finding the most suitable numerical integrator and propagator, to find the shape with the best compromise between three objectives: minimize the heat load on the vehicle, maximize its payload volume, and maximize the ground track of the system during re-entry.
\end{zitemize}
\item Literature study: Application of Taylor Series Integration to an astrodynamics trajectory to a binary asteroid system such as HERA. 

\end{zitemize}
\subsection{{Grado en Ingeniería Aeroespacial} \hfill	09 2015 --- 07 2019} \subtext{School of Aeronautical and Space Engineering (ETSIAE), Technical University of Madrid (UPM) \hfill Madrid, Madrid, Spain} 
\begin{zitemize}
\item Specialization: Aerospace Science and Technology (7.14)
\item Key courses: optimisation Theory (9.4), Complex Analysis (9.5), Orbital Mechanics, Lagrangian Mechanics, Flight
Mechanics, Rocket Propulsion, Space Flight, Vibrations.
%\item Key projects: 
%\begin{zitemize}
%\item Numerical propagation of Heat Equation in a two-dimensional plate resembling fast-cooling of a rotor blade.
%\item Numerical minimization of the free energy in a fluid, equivalent to minimizing the shape of a soap bubble holded by two circumferences. The analytical solution was known, a catenoid.
%\item Design of the control system of a racing drone usign a PD controller. 
%\end{zitemize}

\item Internship in the Department of Applied Mathematics working with open source platforms FEnics, Python, and
Paraview. Dissertation (Trabajo Fin de Grado, TFG): Implementation of a compressible Navier-Stokes solver using FEnics. 

\end{zitemize}
